\chapter{Einleitung}
\label{einleitung}

Homepage\footnote{\url{https://github.com/rusty1s/embedded\_gcnn}}

Insbesondere hier schon auf räumlich und spektral eingehen, da es woanders keinen sinn macht

In the context of the generalization of Convolutional Neural Networks (CNNs) to irregular domains modelled by graphs, the problem is the classification or regression of graph signals, i.e.\ signals who take a value at each vertex of a weighted graph. There is two approaches to convolve a graph signal with a (learned) filter:
Spatially sliding a filter on the vertices, as you would slide a filter on a 2D image or a 1D audio signal (the pixels form a grid graph, the time forms a line graph), i.e.\ the straightforward application of the definition of a convolution. This approach however presents two challenges: (1) the definition of a receptive field / neighbourhood, because sampling on arbitrary graphs is not necessarily uniform and (2), the ordering of nodes, because problem-specific ordering, e.g.\ spatially ordered pixels or time ordered samples, is missing. These recent works, who present the same ideas differently, spatially define the convolution operator on graphs:
The spectral formulation builds on Spectral Graph Theory and Computational Harmonic Analysis. It decomposes the graph Laplacian (via an eigendecomposition) to form a Fourier basis, which properties are analog to the classical Fourier basis on n-dimensional Euclidean spaces. A convolution in the graph domain is then equivalent to a multiplication in the spectral domain. See [1211.0053] for an overview of the Graph Signal Processing field. Note that the spectral approach was also proposed in [1312.5851] (using FFTs) to speed up CNNs on regular 2D Euclidean spaces (i.e.\ for images). The limitations of this approach is (for now, we have plans to address those): (1) filters are rotation invariant, and (2) filters are not directly transferrable to a different graph. These recent works, who build on one another, spectrally define the convolution operator on graphs:

\input{kapitel/einleitung/problemstellung}
\input{kapitel/einleitung/aufbau}
